\section{Design Objectives}

Based on our task analysis, we come up with these design objectives for CAnalytics.

\subsection{O1. Integrating data modeling, data analysis, and hypothesis development}
CAnalytics aims to enable an all-in-one workspace for intelligence analysis. Analysts should be able to smoothly transit from one activity to another, without technical boundaries. Data models created from documents can be directly visualized and analyzed, and be extended in hypothesis development.
\subsection{O2. Enabling collaborative hypotheses development}
An objective is to enable hypothesis development and sharing. While simply sharing hypotheses is beneficial to analysis teams, its positive impact is limited to an extent as it is not completely leveraging the various expertise of a team. Where instead, the combining and evolving of hypotheses from and by multiple members of the team (where the evidence that the hypothesis is based on is included in the hypothesis object) creates an environment where the team is more than just a sum of its parts.
we will help analysts to share their insights/hypotheses with supporting visualization early in the process. To impart knowledge, visualizations conveniently improve the understanding of complex problems. When users are exploring the visualization and find an insight, they will be able to share the insight together with the grounding visualization. The visualization will be interactive rather than a static screenshot, keeping the ad hoc visualization state. 
Insofar as stating unknowns is a difficult task, at least making what analysts do know more explicit and the assumptions that they made increases a large amount of transparency into their analysis
\subsection{O3. Facilitating evidence marshaling}
Our design should allow users to examine evidence from multiple aspects. For example, temporal visualization helps analysts keep track of temporal evolution of events, so that they can identify patterns of timing if any. Proximity-based projections, where closely related insights are visually presented as clusters, assist users in identifying activities in the same area. Interactions should be provided to coordinate these views so that users can effectively navigate among these evidence views, and piece them together to obtain insights.
\subsection{O4. Supporting information sharing and team awareness}
We propose to enable real time data sharing and explicit awareness support. Analysts should be able to share source documents, annotated evidence, patterned views, and hypotheses and insights in real time. Partners can verify who identified and shared the information, and can validate against the source document to confirm sanity. One’s activities should be transparent to teammates without extra effort, so that everyone is aware of other’s activities. 
\subsection{O5. Capturing team actions for research purposes}
The system captures and relays user actions to teammates to support team awareness. Meanwhile, CAnalytics can collect and save these actions for research purposes. User operations in the system provides an opportunity to investigate in detail team behavior in collaborative intelligence analysis. One objective of CAnalytics is to utilize it as a research instrument to collect team behaviors. We can capture user actions as they interact with the system, which will act as a window into team cognitive process. 
