\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[]{biblatex}
\addbibresource{../../Bibliography/Dissertation.bib}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\section{Related work}\label{related-work}


Many studies have been reported to investigate specific design features
to support collaborative information analysis. For example, Goyal and
Fussell \autocite{Goyal2016} studied the effect of hypotheses sharing on
sensemaking. Mahyar and Tory \autocite{Mahyar2013b} designed a
visualization to connect collaborators' common findings and evaluated
its support for team performance. Hajizadeh et al.
\autocite{Hajizadeh2013} explored how sharing teammate's interactions
affects awareness. These studies report interesting results of
controlled lab studies to validate hypotheses of specific design
features. However, they do not provide insight on how teams would
collaborate with a complete tool as nexus of features in the real world
over extended period of time.

Field studies were conducted aimed to understand design requirements of
collaborative information analysis in more realistic settings. Chin et
al. \autocite{Chin2009} observed and analyzed the analytic strategies,
work practices, tools ad collaboration norms of professional
intelligence analysts. Kang and Stasko \autocite{Kang2011} studied how
student analysts, as in our study, completed in-class intelligence
projects. Carroll et al. \autocite{Carroll2013} attempted to model a
complex analytic task scenario in a lab setting, and examined the
development of team awareness in a four-hour-long task. These studies
helped improve understanding of current work practice with
state-of-the-art tools or no tools at all. We built our tool based upon
their study findings, and pursue to further explore design implications
by investigating tool usage in a similar naturalist environment.

Our study took place during the 10th week of the course. Before that
students learned several analytic techniques, including IEW (a technique
to extract and assess values of evidence), ACH (a technique to evaluate
multiple hypotheses against evidence), timeline analysis and network
analysis, as well as state-of-the-art tools to facilitate these
techniques. Two weeks before our study, students practiced applying
these techniques in a hands-on project. A typical workflow started with
IEW to extract and model data from documents. Students then replicated
key facts into analytic artifacts such as an ACH Matrix in PARC ACH, a
timeline and a network graph in Analyst's Notebook. They had to repeat
the process for each different tool because the data cannot be shared
and carried over directly. Most tools they used lacked serious
collaboration support (except that some teams used Google Doc to
construct an IEW table). Analysts were unable to contribute
simultaneously (known as production blocking \autocite{Diehl1987a}). The
analysis work was often divided by tools: each individual created and
analyzed an artifact with a tool on their own. This had the consequence
that findings and hypotheses be made without integrating collective
efforts and diverse knowledge. Analysts must coordinate work by manually
sharing notebooks or graphs, resulting in a scattered placement of
results, requiring repeated manual resynchronizing to identify redundant
or missing pieces of information, analysis of information, and analytic
hypotheses. The instructor and students in our study were aware of the
shortcomings of available tools with respect to support of
collaboration.

\printbibliography

\end{document}
